%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Student Researcher, Instructor, and Mentor} % Job title
    {Laboratory of Molecular Simulation (UC Berkeley, Berend Smit Group)} % Organization
    {Berkeley, CA} % Location
    {Jan. 2015 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item { \eyecatch{Applied transfer reinforcement learning techniques} and data-driven approaches for optimal control of cold atmospheric plasma.}
		\item { \eyecatch{Trained deep neural network models} of atomic interactions in zeolites to significantly reduce the computational expense of molecular dynamics simulations while retaining quantum chemical accuracy.}
        \item {\eyecatch{Coded a recursive, minimal cut graph theory algorithm} to perform high-throughput data analysis and identify zeolite framework materials with previously unrecognized potential for synthesis as 2-dimensional water desalination membranes.}
        \item {\eyecatch{Derived and programmed enhanced Monte Carlo sampling schemes} to efficiently generate more and better statistical information when performing high-throughput materials screening for adsorption applications involving flexible chain molecules.}
        \item {\eyecatch{Utilized cheminformatics and computer vision techniques} to perform hypothetical crystal structure prediction in the search for novel, high-performing adsorbents.}
        \item {\eyecatch{Developed statistical physics models and high-throughput screening techniques} to identify systematic biases that arise when simulating adsorption in flexible materials.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Process Engineering Intern} % Job title
    {General Electric, Inc.} % Organization
    {Twinsburg, OH} % Location
    {Jun. 2013 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\eyecatch{Coded VBA applications} to automate the Returned Materials Authorization process and capitalize on an underutilized \$20 MM Enterprise Resource Planning investment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Customer Management Co-op} % Job title
    {Janssen (A Pharmaceutical Company of Johnson \& Johnson)} % Organization
    {Raritan, NJ} % Location
    {Jun. 2012 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\eyecatch{Wrote VBA programs to optimize data acquisition and demand planning analysis} for the US Sales \& Operations supply chain team to improve reporting accuracy and reduce monthly man hour requirements by 80\% in a constrained work stream.}
        \item {\eyecatch{Managed the monthly Executive Sales \& Operations Planning Dashboard:} automated the identification of poor alignments between financial and operating forecasts of Janssen's multi-billion dollar Tier 1 product portfolio to create actionable intelligence for the North America leadership team.}
        \item {\eyecatch{Implemented an automated statistical forecasting tool} to monitor over 200 established pharmaceutical products which yielded improved forecast/demand alignment and inventory levels.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {PSU Department of Chemical Engineering (Enrique Gomez Group)} % Organization
    {State College, PA} % Location
    {Jun. 2011 - Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\eyecatch{Constructed a block co-polymer organic photovoltaic device} with record 3\% efficiency due to a microphase separated active layer.}
	    \item {\eyecatch{Built, tested, and optimized} organic electronic devices such as photovoltaic cells and transistors for 2+ years.}        
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
